Plots

### 2025-02-25 src/plots.Rmd
Collect titles

# Plot perf for pccc
plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    title = paste0(cod_adult, " Causes of Death for ", n_adult, " Adult Records")
) /
    plot_perf(
        df_long %>% filter(age == "child"),
        calc_pccc,
        title = paste0(cod_child, " Causes of Death for ", n_child, " Child Records")
    ) /
    plot_perf(
        df_long %>% filter(age == "neo"),
        calc_pccc,
        title = paste0(cod_neo, " Causes of Death for ", n_neo, " Neonatal Records")
    ) +
    plot_layout(heights = c(2, 1, 1))

>>>>

# Plot perf for pccc
plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    title = paste0("(a) Adult Records (n=", n_adult, ")"),
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    y_title = "Cause of Death"
) /
    plot_perf(
        df_long %>% filter(age == "child"),
        calc_pccc,
        title = paste0("(b) Child Records (n=", n_child, ")"),
        x_title = "Partial Chance Corrected Concordance (PCCC)",
        y_title = "Cause of Death"
    ) /
    plot_perf(
        df_long %>% filter(age == "neo"),
        calc_pccc,
        title = paste0("(c) Neonatal Records (n=", n_child, ")"),
        x_title = "Partial Chance Corrected Concordance (PCCC)",
        y_title = "Cause of Death"
    ) +
    plot_layout(
        heights = c(2, 1, 1),
        axis_titles = "collect"
    )
